
---
output: github_document
---

**DD measure of democracy**: The raw data file `ddrevisited_data_v1.dta` comes from [https://sites.google.com/site/joseantoniocheibub/datasets/democracy-and-dictatorship-revisited](https://sites.google.com/site/joseantoniocheibub/datasets/democracy-and-dictatorship-revisited).

**Polity IV measure of democracy**: The raw data file `p4v2018.xls` comes from [http://www.systemicpeace.org/inscrdata.html](http://www.systemicpeace.org/inscrdata.html).

# File Organization

```
cool-project/
├── R/
│   ├── clean-data.R
│   ├── fit-models.R
│   ├── make-table.R
│   └── plot-data.R
├── data/
│   ├── raw/
│   │   ├── ddrevisited_data_v1.dta
│   │   └── p4v2018.xls
│   ├── clean-data.csv
│   └── clean-data.rds
├── doc/
│   ├── fig/
│   │   └── plot1.png
│   ├── tab/
│   │   └── table.tex
│   ├── cool-project.pdf
│   └── cool-project.tex
├── output/
│   ├── model-fit.csv
│   ├── model-fit.rds
│   ├── model-pred.csv
│   └── model-pred.rds
├── README.md
└── cool-project.Rproj
```

# Review Exercises for Reading Data Sets Into R

There are 8 total data sets in `cool-project/` (all the files in `data/` and `output/`). Answer the following questions for each data set:

1. What function should you use to read that file?
1. What's the working directory?
1. What's the path (relative to the working directory)?
1. Given the above, what's the code to read the data (and store it as an object)?

# Solutions 

## `ddrevisited_data_v1.dta`

1. The `.dta` extension indicates that this is a Stata data set, so I should use the `read_dta()` function in the haven package.
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `data/raw/ddrevisited_data_v1.dta`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(haven)  # needed for read_dta()

# load raw data set
raw_df <- read_dta("data/raw/ddrevisited_data_v1.dta")
```

## `p4v2018.xls`

1. The `.xls` extension indicates that this is a Excel spreadsheet, so I should use the `read_excel()` function in the readxl package. But because this is an Excel spreadsheet, who knows what will happen.
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `data/raw/dp4v2018.xls`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(readxl)  # needed for read_dta()

# load raw data set
raw_df <- read_excel("data/raw/p4v2018.xls")
```

## `clean-data.csv`

1. The `.csv` extension indicates that this is a comma-separated or CSV data set, so I should use the `read_csv()` function in the readr package (that is part of tidyverse). 
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `data/clean-data.csv`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  # automatically loads readr, needed for read_csv()

# load clean data set
df <- read_csv("data/clean-data.csv")
```

## `clean-data.rds`

1. The `.rds` extension indicates that this is an R data set, so I should use the `read_rds()` function in the readr package (that is part of tidyverse). 
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `data/clean-data.rds`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  # automatically loads readr, needed for read_rds()

# load clean data set
df <- read_rds("data/clean-data.rds")

# a little something extra, in case you're curious what the clean data set
# looks like. it contains the polity_iv and dd measures of democracy
glimpse(df)
```

## `model-fit.csv`

1. The `.csv` extension indicates that this is a comma-separated or CSV data set, so I should use the `read_csv()` function in the readr package (that is part of tidyverse). 
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `output/model-fit.csv`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  # automatically loads readr, needed for read_csv()

# load clean data set
fit_df <- read_csv("output/model-fit.csv")
```
## `model-fit.rds`

1. The `.rds` extension indicates that this is an R data set, so I should use the `read_rds()` function in the readr package (that is part of tidyverse). 
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `output/model-fit.rds`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  # automatically loads readr, needed for read_rds()

# load clean data set
fit_df <- read_rds("output/model-fit.rds")

# a little something extra, in case you're curious what this "model fit"
# data set looks like (is a regression of polity_iv on dd)
glimpse(fit_df)
```

## `model-pred.csv`

1. The `.csv` extension indicates that this is a comma-separated or CSV data set, so I should use the `read_csv()` function in the readr package (that is part of tidyverse). 
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `output/model-pred.csv`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  # automatically loads readr, needed for read_csv()

# load clean data set
pred_df <- read_csv("output/model-pred.csv")
```

## `model-pred.rds`

1. The `.rds` extension indicates that this is an R data set, so I should use the `read_rds()` function in the readr package (that is part of tidyverse). 
1. The working directory is `cool-project/` because the working directory is always the project directory since I use an `.Rproj` file to manage my projects.
1. The path is `output/model-pred.rds`. I can see this in the directory tree above, by inspecting the directory on my computer (e.g., Finder for macOS), or by inspecting the *Files* tab in the lower-right window in RStudio.
1. Below:

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  # automatically loads readr, needed for read_rds()

# load clean data set
pred_df <- read_rds("output/model-pred.rds")

# a little something extra, in case you're curious what this "prediction fit"
# data set looks like (from a regression of polity_iv on dd)
glimpse(pred_df)
```